---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ChartCompletion

The goal of this project is to visualize chart completion rates over time and drive understanding of what interventions led to improvements. For demonstration purposes, all names have been replaced by fictional names.

## Rationale
Documentation (charts) should be completed in a timely manner, ideally within 24 hours. Delays in completion result in greater risk for documentation errors, incomplete information provided for ongoing care, delays in billing collection, and lost revenue. Staff typically work on a four day rotation, so the key measures are the percent open more than 24 hours, more than four days, and more than eight days. The numerators are the number of charts open for each period of time and the denominator is the number of charts started within the past thirty days.

## Key Visualization
The key visualization charts these rates on a day-by-day basis using rolling 30-day windows. The graph also highlights the most reecent rate numbers in individual callout gems on the right. This chart is useful when correlated with knowledge of external events to understand what interventions drive significant improvements.

```{r performance_over_time, echo=FALSE, fig.height=7, fig.width=12, message=FALSE, warning=FALSE}
library(ChartCompletion)
graph_chart_stats()
```
Looking at individual employees highlights which individuals have substantially worse performance as well as to understand individual performance over time. This can be correlated with external events, such as training periods, times of external stress such as illnesses or divorces, and individual work loads. An individual with a season of poor performance correlated with an external stressor that self-resolved is typically not someone that needs additional help, while an individual with significant poor performance likely needs help to catch up and coaching to avoid getting behind in the future.
```{r per_provider_performance, echo=FALSE, fig.height=24, fig.width=12, message=FALSE, warning=FALSE}
graph_chart_by_provider()
```

Using this approach can identify the worst performers, and these can be removed to get a better sense of the overall performance.

```{r time_performance_filtered, echo=FALSE, fig.height=7, fig.width=12, message=FALSE, warning=FALSE}
graph_chart_stats(remove_worst_performers = 10)
```

```
